Kronos \& Krios: Evidence for accretion of a massive, rocky planetary system in a comoving pair of solar-type stars

### 2017-09-08 paper/ms.tex
missed notation change

We take the solar abundances, $\elemH{X}$, of element \elem{X}
(\citealt{Asplund:2009aa}) which can be converted to mass fraction as
\begin{equation}
  f_{X,\mathrm{photo}} = \frac{10^{\elemH{X}} m_X}{\Sigma_X 10^{\elemH{X}} m_X}
\end{equation}
where $m_X$ is the mass of each element in e.g., atomic mass unit.
Assuming that the added material has a total mass $M_\mathrm{add}$, and the
mass fraction in each element $f_{X,\mathrm{add}}$,
the abundance difference is
\begin{equation}
  \Delta\elemH{X} = \log_{10} \frac{f_{X,\mathrm{photo}}\,f_\mathrm{CZ}\,M_\mathrm{star}
    + f_{X,\mathrm{acc}}\,M_\mathrm{acc}}
    {f_{X,\mathrm{photo}}\,f_\mathrm{CZ}\,M_\mathrm{star}}
\end{equation}
where $f_\mathrm{CZ}$ is the fraction of the star's mass in the convective envelope.
We assume $f_\mathrm{CZ} = 0.02$ (\citealt{2013ApJ...776...87S}),
and take the composition of bulk Earth from a chondritic model of the Earth
(\citealt{2003TrGeo...2..547M}).
Similar calculations have been performed by e.g., \citet{Chambers:2010aa},
\citet{Mack:2014aa,Mack:2016aa}.

>>>>

We take the solar abundances, $\elemH{X}$, of element \elem{X}
(\citealt{Asplund:2009aa}) which can be converted to mass fraction as
\begin{equation}
  f_{X,\mathrm{photo}} = \frac{10^{\elemH{X}} m_X}{\Sigma_X 10^{\elemH{X}} m_X}
\end{equation}
where $m_X$ is the mass of each element in e.g., atomic mass unit.
Assuming that the accreted material has a total mass $M_\mathrm{acc}$, and the
mass fraction in each element $f_{X,\mathrm{acc}}$,
the abundance difference is
\begin{equation}
  \Delta\elemH{X} = \log_{10} \frac{f_{X,\mathrm{photo}}\,f_\mathrm{CZ}\,M_\mathrm{star}
    + f_{X,\mathrm{acc}}\,M_\mathrm{acc}}
    {f_{X,\mathrm{photo}}\,f_\mathrm{CZ}\,M_\mathrm{star}}
\end{equation}
where $f_\mathrm{CZ}$ is the fraction of the star's mass in the convective envelope.
We assume $f_\mathrm{CZ} = 0.02$ (\citealt{2013ApJ...776...87S}),
and take the composition of bulk Earth from a chondritic model of the Earth
(\citealt{2003TrGeo...2..547M}).
Similar calculations have been performed by e.g., \citet{Chambers:2010aa},
\citet{Mack:2014aa,Mack:2016aa}.
